---
title: "Does Noodle the Pug Have Bones?"
author: "Eric R. Scott"
output: 
   html_document: 
    toc: yes
    toc_float: yes
    number_sections: no
    highlight: kate
    theme:
      version: 4
      bootswatch: flatly
---
*last updated `r Sys.Date()`*

```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

Load packages:

```{r}
library(googlesheets4)
library(janitor)
library(tidyverse)
library(lubridate)
library(broom)
library(car)
library(gt)
theme_set(theme_bw())
```

# Data Source

I've compiled the results of #BonesNoBones in a [Google Sheet](https://docs.google.com/spreadsheets/d/1Qi4YjmEu6pYpUI-Tnu4h1I2gJNfPRWztaObV9ZNLb5o/edit#gid=0) that can be read in with `read_sheet()` from the `googlesheets4` package.


```{r}
noodle <- 
  read_sheet("1Qi4YjmEu6pYpUI-Tnu4h1I2gJNfPRWztaObV9ZNLb5o") %>%
  clean_names()
head(noodle)
```

# Overall probability of bones

```{r}
total_bones <- 
  noodle %>% 
  summarize(bones = sum(bones == "yes")/n())
total_bones
```

The overall chance of a bones day is `r round(total_bones$bones * 100)`%.

# Bones days by day of week

Are bones more or less likely depending on the day of the week?

```{r}
noodle <- 
  noodle %>% 
  mutate(dow = wday(date, label = TRUE))

by_dow <- 
  noodle %>% 
  group_by(dow) %>% 
  summarize(total_readings = n(),
            bones = sum(bones == "yes") / total_readings) 
gt(by_dow)
```

It looks like bones are more likely on some days than others.

```{r}
ggplot(by_dow, aes(x = dow, y = bones)) +
  geom_col(fill = "darkblue") + 
  labs(x = "Day of Week", y = "P(bones)")
```

# Trend in bones?

Is there any trend over time in the probabilty of Noodle having bones?

```{r}
noodle <- 
  noodle %>% 
  mutate(bones_bin = case_when(bones == "yes" ~ 1L,
                               bones == "no" ~ 0L,
                               TRUE ~ NA_integer_))

ggplot(noodle, aes(x = date, y = bones)) +
  geom_jitter(width = 0, height = 0.1)
```

Looks like it would make sense to only focus on recent points, since poor sampling before July 2021

```{r}
noodle_subset <- noodle %>% filter(date > mdy("July 1, 2021"))

```


```{r}
noodle_m <- glm(bones_bin ~ date, family = binomial, data = noodle_subset)
car::Anova(noodle_m)
```
```{r}
augment(noodle_m, type.predict = "response", se_fit = TRUE) %>% 
  ggplot(aes(x = date)) +
  geom_line(aes(y = .fitted)) +
  geom_ribbon(aes(ymin = .fitted - .se.fit, ymax = .fitted + .se.fit), alpha =0.4) +
  geom_point(aes(y = bones_bin), alpha = 0.5, shape = 108, size = 5) +
  labs(y = "P(bones)")
```

Probability of bones is increasing over time, but not significantly so.

